---
title: "Untitled"
author: "Shay Iyer"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plyranges)
library(trackViewer)
```

```{r}
merge <- read_csv("/Volumes/sheynkman/projects/shay_thesis/BIO334_output/tmp/LR_data/mergefoxp1.csv")
```


```{r}
map.folder <- "/Volumes/sheynkman/projects/shay_thesis/BIO334_output/out/mapdata"
se.map.path <- paste(map.folder, "/se_map.csv", sep = "")
mxe.map.path <- paste(map.folder, "/mxe_map.csv", sep = "")
a3ss.map.path <- paste(map.folder, "/a3ss_map.csv", sep = "")
a5ss.map.path <- paste(map.folder, "/a5ss_map.csv", sep = "")
```

```{r}
se.map <- read_csv(se.map.path)
mxe.map <- read_csv(mxe.map.path)
a3ss.map <- read_csv(a3ss.map.path)
a5ss.map <- read_csv(a5ss.map.path)

rm(se.map.path, mxe.map.path, a3ss.map.path, a5ss.map.path)
```

```{r}
all.map <- rbind(se.map, mxe.map, a3ss.map, a5ss.map) %>% data.frame(check.names = TRUE)
```

```{r}
all.map$eventID <- as.character(all.map$eventID)
```


```{r}
all.map <- mutate(all.map, type = ifelse(grepl("se",eventID), "se",
                                     ifelse(grepl("mxe",eventID), "mxe",
                                            ifelse(grepl("a3ss",eventID), "a3ss",
                                                   ifelse(grepl("a5ss",eventID), "a5ss", "nulltype")))))
```

```{r}
all.map <- mutate(all.map, transcript_status = ifelse (grepl("ENCLB", transcript_id), "novel", "known"))

all.map <- all.map %>% mutate(
  "transcript_dTPM" = lr_tpm_c1 - lr_tpm_c2
)

all.map <- all.map %>% mutate(
  eventform = ifelse(grepl("inc", eventID), "inclusion", "exclusion")
)
```


```{r}
all.map.foxp1 <- all.map %>% filter(gene_name != "FOXP1-IT1" & gene_name != "FOXP1-AS1")
```

```{r}
all.map.summary <- all.map.foxp1 %>% select(transcript_id, transcript_status) %>% summarize(transcript_id_group = transcript_id, transcript_status = transcript_status) %>% unique()

all.map.summary.tstatus <- all.map.summary %>% group_by(transcript_status) %>% summarize(n = n())

n_type <- all.map.foxp1 %>% select(eventID, type) %>% unique() %>% group_by(type) %>%  summarize(n = n())
```

> 76 known transcripts that had at least one event mapped to them, 10 novel transcripts that had at least one event mapped to them. 19 distinct events were mapped to these transcripts. 

```{r}
all.map.sumstats <- all.map.foxp1 %>% group_by(type, gene_name) %>% summarize(n_typeinstance = n())

total <- 172 + 86 + 103 + 763

all.map.sumstats$prop <- (all.map.sumstats$n_typeinstance/total)

all.map.sumstats$n_type <- n_type$n 

all.map.sumstats.incexc <- all.map.foxp1 %>% group_by(type, eventform, gene_name) %>% summarize(ntype = n())
```



```{r}
all.map.foxp1 %>% select(transcript_id) %>% unique() %>% summarize (n = n())
```

```{r}
ggplot(all.map.sumstats, aes(x = type, y = prop, fill = type)) + geom_col() + 
  scale_y_continuous(labels = scales::percent, "Percent of map events") + 
  xlab("Event type") + 
  ggtitle(label = "Figure 4: Distribution of event-to-transcript maps for FOXP1", subtitle = "Black label corresponds to number of unique events") +
  geom_text(aes(label = n_type), vjust = 1.5, colour = "black")
```

```{r}
ggplot(all.map.sumstats) + geom_col(aes(x = gene_name, y = ntype, fill = eventform))
```

```{r}
all.map.foxp1 %>% head()
```

```{r}
all.map.foxp1 %>% select(transcript_id, transcript_dTPM) %>% unique() %>% filter(transcript_dTPM != 0)
```

```{r}
foxp1.known.enst <- c("ENST00000649528.1", "ENST00000650231.1", "ENST00000614176.5", "ENST00000648748.1", "ENST00000649695.1", "ENST00000650387")
```

```{r}
all.map.foxp1.known <- all.map.foxp1 %>% filter(transcript_id %in% foxp1.known.enst)
```

```{r}
known.mxe <- all.map.foxp1.known %>% filter(type == "mxe")

mxe.transcripts <- known.mxe$transcript_id

merge.mxe <- merge %>% filter(transcript_id %in% mxe.transcripts)
```

```{r}
mxe.events <- read_csv("/Volumes/sheynkman/projects/shay_thesis/BIO334_output/tmp/SR_data/MXE.csv")
```

```{r}
mxe.6043 <- mxe.events %>% filter(geneSymbol == "FOXP1") %>% filter(grepl('6043', ID))
```

	
```{r}

```

mxe.6043.exc
junction coords <- 70970805-70972554:70972676-70976940 

```{r}
merge.ENST649528 <- merge %>% filter(transcript_id == "ENST00000649528.1")
```

```{r}
mxe.map <- mxe.map %>% filter(gene_name == "FOXP1")
```


```{r}
a3ssmap.649528 <- a3ss.map %>% filter(transcript_id == "ENST00000649528.1")
```

a3ss.7984.exc is candidate co-actor

```{r}
a3ss.events <- read_csv("/Volumes/sheynkman/projects/shay_thesis/BIO334_output/tmp/SR_data/A3SS.csv")
```

```{r}
a3ss.events.7984 <- a3ss.events %>% filter(ID == "a3ss.7984")
```

```{r}
merge.ENST649528.exons <- merge.ENST649528 %>% filter(feature == "exon") %>% select(gene_name, transcript_id, exon_number, start, end, seqname, strand)

merge.ENST649528.exons <- merge.ENST649528.exons %>% mutate("width" = (end - (start-1)))

merge.ENST649528.exons.iranges <- merge.ENST649528.exons %>% select(start, end, width)
```

```{r}
iranges_ENST <- as_iranges(merge.ENST649528.exons.iranges)
```

```{r}
grange_ENST <- GRanges(seqnames = merge.ENST649528.exons$seqname, ranges = iranges_ENST, strand = merge.ENST649528.exons$strand)
```

```{r}
# plotGRanges(range = grange_ENST) doesn't work
```

```{r}
all.map.ENST <- all.map %>% filter(transcript_id == "ENST00000649528.1")
```

